\input{title.tex}

### 2023-07-28 docs/papers/04_response_letter/source/reviewer_1.tex
fix(method): :memo: "placebo test"

\AR{} Basically, yes, ``Placebo'' is a term.

\subsection{Other comments}\label{sec:1-3}
% 本研究中使用的数据似乎有不同的时间段，大多数数据来自2013年之前。近十年来，黄河的水文状况和水治理应该发生了重大变化。因此，结合近十年的结果将使这项研究更加可靠。
\RC{} I would change the first two key points into full sentences; as they are, they are only fragments, while the third and fourth points are full sentences.

>>>>

\AR{} Basically, the term ``placebo'' is indeed used in this context in the literature, particularly in policy evaluation studies where the synthetic control method is used. It refers to the procedure of applying the synthetic control method to units that did not receive treatment to verify the significance of the estimated treatment effects. This procedure is called a ``placebo test'' or ``placebo experiment'' and is crucial for validating the results of synthetic control analyses.

\AR*{} In light of your comment, we have revised our manuscript to consistently use the term ``placebo tests'' throughout, and we have added references that use this term in a similar context~\cite{abadie2010}. We hope this change addresses your concern and provides a clear explanation of the term's usage:

\begin{quote}[page=XXX, sline=XXX, eline=XXX]
    Secondly, placebo tests are another common way to evaluate the effectiveness of synthetic control methods~\cite{abadie2010}.
\end{quote}

\subsection{Other comments}\label{sec:1-3}

\RC{} I would change the first two key points into full sentences; as they are, they are only fragments, while the third and fourth points are full sentences.
